Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-16 doc/manuscript/ESSDmanuscript.Rmd
add increment variables
#6

**Here, we**
(1) clarify definitions of relevant carbon stocks and increments
(2) describe mapping of ForC to IPCC's EFDB,
(3) describe updates to ForC  (ForC v4.0),
(4) summarize the data in ForC that's relevant to EFDB, identifying gaps, and
(5) provide recommendations for improving data collection, analysis, database, and accounting.

@@

To support export of data to EFDB, and to improve the overall quality of the ForC database, we implemented some modest restructuring, resolved duplicate records, and conducted quality control.
This section describes changes relative to ForC v2.0 [@anderson-teixeira_forc_2018].

>>>>

**Here, we**
(1) review definitions of relevant carbon stocks and increments
(2) describe mapping of ForC to IPCC's EFDB,
(3) describe updates to ForC  (ForC v4.0),
(4) summarize the data in ForC that's relevant to EFDB, identifying gaps, and
(5) provide recommendations for improving data collection, analysis, database, and accounting.

@@

To support export of data to EFDB, and to improve the overall quality of the ForC database, we added ## increment variables, implemented some modest restructuring, resolved duplicate records, and conducted quality control.
This section describes changes relative to ForC v2.0 [@anderson-teixeira_forc_2018].

## Increment variables
We added ## increment variables to the set of named and defined variables. 
*(https://github.com/forc-db/IPCC-EFDB-integration/issues/6)*
These are directly related to C stocks as previously defined in ForC, with "*delta.*" added in front of the variable name.

Although these variables currently lack records, the structure exists such that records can be populated over time.

### 2021-06-16 doc/manuscript/ESSDmanuscript.tex
add increment variables
#6

\textbf{The International Panel on Climate Change (IPCC) provides
guidance for national greenhouse gas (GHG) inventories for reporting to
the United Nations Framework Convention on Climate Change \citep[UNFCCC,
(REFS for older guidelines),][]{ipcc_2019_2019}.} Under this guidance,
GHG inventories are to include all managed land, including most of the
world's forest land \citep{ogle_delineating_2018}. The IPCC inventory
guidelines include specific instructions for accounting for forest land
\ldots{} \citep{ipcc_agriculture_2006, ipcc_2019_2019a}. This guidance
has improved as more of the relevant underlying data has become
available \citep{requenasuarez_estimating_2019}, but there remains room
for continuous improvement as the science advances. For example,
\citet{cook-patton_mapping_2020} \emph{(summarize IPCC comparison
results)}. \emph{Moreover, it is useful for those compiling national
greenhouse gas inventories to have access to locally-specific
information, when available.} To improve the data accessible for C
accounting, the IPCC created the Emission Factor Database (EFDB;
https://www.ipcc-nggip.iges.or.jp/EFDB/main.php), which is intended as a
recognized library of emission factors and other parameters that can be
used for estimating greenhouse gas emissions and removals.

@@

\textbf{Here, we} (1) clarify definitions of relevant carbon stocks and
increments (2) describe mapping of ForC to IPCC's EFDB, (3) describe
updates to ForC (ForC v4.0), (4) summarize the data in ForC that's
relevant to EFDB, identifying gaps, and (5) provide recommendations for
improving data collection, analysis, database, and accounting.

@@

To support export of data to EFDB, and to improve the overall quality of
the ForC database, we implemented some modest restructuring, resolved
duplicate records, and conducted quality control. This section describes
changes relative to ForC v2.0 \citep{anderson-teixeira_forc_2018}.

>>>>

\textbf{The International Panel on Climate Change (IPCC) provides
guidance for national greenhouse gas (GHG) inventories for reporting to
the United Nations Framework Convention on Climate Change \citep[UNFCCC,
(REFS for older guidelines),][]{ipcc_2019_2019}.} Under this guidance,
GHG inventories include all managed land, including most of the world's
forest land \citep{ogle_delineating_2018}. The IPCC inventory guidelines
include specific instructions for accounting for forest land \ldots{}
\citep{ipcc_agriculture_2006, ipcc_2019_2019a}. This guidance has
improved as more of the relevant underlying data has become available
\citep{requenasuarez_estimating_2019}, but there remains room for
continuous improvement as the science advances. For example,
\citet{cook-patton_mapping_2020} \emph{(summarize IPCC comparison
results)}. \emph{Moreover, it is useful for those compiling national
greenhouse gas inventories to have access to locally-specific
information, when available.} To improve the data accessible for C
accounting, the IPCC created the Emission Factor Database (EFDB;
https://www.ipcc-nggip.iges.or.jp/EFDB/main.php), which is intended as a
recognized library of emission factors and other parameters that can be
used for estimating greenhouse gas emissions and removals.

@@

\textbf{Here, we} (1) review definitions of relevant carbon stocks and
increments (2) describe mapping of ForC to IPCC's EFDB, (3) describe
updates to ForC (ForC v4.0), (4) summarize the data in ForC that's
relevant to EFDB, identifying gaps, and (5) provide recommendations for
improving data collection, analysis, database, and accounting.

@@

To support export of data to EFDB, and to improve the overall quality of
the ForC database, we added \#\# increment variables, implemented some
modest restructuring, resolved duplicate records, and conducted quality
control. This section describes changes relative to ForC v2.0
\citep{anderson-teixeira_forc_2018}.

\subsection{Increment variables}

We added \#\# increment variables to the set of named and defined
variables.
\emph{(https://github.com/forc-db/IPCC-EFDB-integration/issues/6)} These
are directly related to C stocks as previously defined in ForC, with
``\emph{delta.}'' added in front of the variable name.

Although these variables currently lack records, the structure exists
such that records can be populated over time.
